\bottomrule
\end{tabular}
\begin{tablenotes} [flushleft]
\item Note: * p$<$0.1, ** p$<$0.05, *** p$<$0.01. Heteroskedasticity robust standard errors in parentheses. The table displays 2SLS regressions of pirate attacks on land conflict events, using ocean wind speed as an instrument. Columns 1, 2, and 3 display the reduced form, first stage, and second stage respectively. In Panel A, no fixed effects are used. In Panel B, region X month X year fixed effects are included. Region effects are the combination of a specific ocean area and a federal ``region", defined by governing body, in Somalia. Panel C includes additional covariates related to weather. Panel C shows wild cluster bootstrap p-values in brackets with Webb weights, a non-studentized test statistic \citep{young2019consistency}, and the test is Anderson-Rubin (AR) \citep{anderson1949estimation}. Panel D includes price covariates (available monthly). The price covariates are for: cattle, daily labor rate, local sesame oil, sugar, wheat flour, camel, charcoal, cowpeas, diesel, firewood, fresh camel milk, goat, grinding cost, imported red rice, kerosene, petrol, red sorghum, salt, sheep, soap, tea leaves, vegetable oil, water drum, wheat grain, and white maize. All panels show the corresponding AR 95\% confidence sets for the IV estimate \citep{anderson1949estimation}, which are efficient for potentially weak instruments, as suggested by \cite{andrews2018weak} and \cite{lee2020F} for just-identified structural equations. 
\end{tablenotes}
\end{threeparttable}
\end{table}
